%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software developer of Dzen - Content and News platform} % Job title
    {VK LLC} % Organization
    {Saint-Petersburg, Russia} % Location
    {Sep. 2023 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Database Migration \& Optimization:} Successfully transferred critical YDB databases from Yandex to VK hosts with zero downtime, handling peak loads of \textbf{40,000 RPS}. Developed a custom data transfer and transfer check mechanism.}
        \item {\textbf{High-Performance Event Processing:} Managed a high-traffic event recording service, processing \textbf{4,000+ RPS} from multiple devices while ensuring reliability and scalability.}
        \item {\textbf{Content Growth Initiatives:} Led projects to attract media authors, implementing key features like \textbf{promoted article pins, comparison tables, and polls} to enhance engagement and direct publishing on the platform.}
        \item {\textbf{Unified Payment System:} Designed and built a \textbf{scalable payment service} from scratch, handling donations, premium, and pro monetization. Streamlined payment processing, reducing dependency to just two developers for maintenance.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software developer of Yandex.Delivery and Yango.Delivery} % Job title
    {Yandex LLC} % Organization
    {Saint-Petersburg, Russia} % Location
    {Jul. 2022 - Sep. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{"Photofixation" Project Leadership:} Successfully designed and implemented a solution to reduce delivery errors by photographing parcels at pickup points, enabling couriers to correctly match shipments, and also reducing legal and financial risks for business partners.}
        \item {\textbf{Complex Batch Delivery Optimization:} Solved courier confusion in multi-stop routes (e.g., mixed A/B point sequences) by introducing visual verification. This innovation \textbf{saved 2M RUB/month} in losses immediately after launch.}
        \item {\textbf{Delivery Confirmation \& Monitoring:} Managed all of "Proof of Delivery" services: Photofixation, Scanner, Custom Instructions, Sms Confirmation. This includes photo uploads, storage, and validation, while overseeing courier timers to ensure SLA compliance.}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Bioinformatics researcher} % Job title
  %   {CT Laboratory} % Organization
  %   {Saint-Petersburg, Russia} % Location
  %   {Jul. 2022 - Sep. 2021} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Investigated the basics of bioinformatics}
  %       \item {Sequenation metagenomes through R technologies and InSilicoSeq}
  %       \item {Analyzed metagenomes with k-mers through KMC3 and Metafast}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
  \cventry
    {Software developer} % Job title
    {Sitronics Group} % Organization
    {Saint-Petersburg, Russia} % Location
    {Sep. 2021 - Jan. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{\url{https://github.com/MrDonaldoWorking/Sitronics-Noise}}
        \item {Investigated filtering process with buffer and proceeded Kalman filtering experiments}
        \item {Researched Kolmogorov-Zurbenko filter applied to Quaternions}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
