%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Python, Telegram API, VK API} % Language, technologies
    {Telegram Bot with user-search in VK} % Project
    {Moscow, Russia} % Location
    {Jan. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Telegram Bot with searching user friends and user photo functionality.}
        \item {\url{https://github.com/Mr-Donaldo/sis_winter_2016_bot}}
      \end{cvitems}
    }

%---------------------------------------------------------
%   \cventry
%     {Assembly}% Language, technologies
%     {Big Integer implementation in Assembly} % Project
%     {Saint Petersburg, Russia} % Location
%     {Mar. 2019} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of experience/contributions/knowledge
%         \item {Big Integer basic arithmetic implemented in assembly language.}
%         \item {\url{https://github.com/MrDonaldoWorking/assembly-tasks}}
%       \end{cvitems}
%     }

%---------------------------------------------------------
  \cventry
    {C++}% Language, technologies
    {Huffman encoder/decoder} % Project
    {Saint Petersburg, Russia} % Location
    {May. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Console utility with compress and decompress functionality using Huffman algorithm.}
        \item {\url{https://github.com/MrDonaldoWorking/Huffman-encoder-and-decoder}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Java, OpenCV}% Language, technologies
    {Video letters recognition} % Project
    {Saint Petersburg, Russia} % Location
    {Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Application showing statistics of learned letters in every different frames in the video file.}
        \item {\url{https://github.com/MrDonaldoWorking/Yandex-Practice}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {C++, PNM}% Language, technologies
    {Picture edition tool} % Project
    {Saint Petersburg, Russia} % Location
    {May. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Basic rotations and mirror functionality.}
        \item {Drawing line with gamma correction and sRGB using Xiaolin Wu's line algorithm}
        \item {Picture dithering algorithms: ordered, random, Floyd-Steinberg, JJN, Sierra-3, Atkinson, Halftone with sRGB and gamma correction.}
        \item {Colour space transformations: RGB / HSL / HSV / YCbCr.601 / YCbCr.709 / YCoCg / CMY.}
        \item {Auto brightness correction functionality.}
        \item {\url{https://github.com/MrDonaldoWorking/Computer-Graphics}}
      \end{cvitems}
    }
    
    %---------------------------------------------------------
  \cventry
    {Python, Decision Tree, AdaBoost}% Language, technologies
    {Object classification visualizer} % Project
    {Saint Petersburg, Russia} % Location
    {Nov. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Application shows steps of how program classifies objects with boosting of decision tree classifier.}
        \item {\url{https://github.com/MrDonaldoWorking/ML-tasks}}
      \end{cvitems}
    }

    %---------------------------------------------------------
  \cventry
    {Java}% Language, technologies
    {Parser Generator} % Project
    {Saint Petersburg, Russia} % Location
    {Feb. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Generates lexer and parser of grammar by checking if grammar is LL(1) and constructing FIRST and FOLLOW sets.}
        \item {\url{https://github.com/MrDonaldoWorking/Lab-Code/tree/master/MT Lab/4}}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {React, Node.js, Playwright, Mockito, Java 11, Spring boot, PostgreSQL, Docker, GitHub Action}% Language, technologies
    {Full Stack Application} % Project
    {Saint Petersburg, Russia} % Location
    {Jan. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Anime site with authentication}
        \item {\url{https://github.com/MrDonaldoWorking/Anime-site}}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {C\#, Unity, .NET Core}% Language, technologies
    {Noise Filtering for VR headset} % Project
    {Saint Petersburg, Russia} % Location
    {May. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Extrapolation when lost connection}
        \item {Filtering constant noises}
        \item {Filtering sudden noises}
        \item {\url{https://github.com/MrDonaldoWorking/Sitronics-Noise}}
      \end{cvitems}
    }

    
%---------------------------------------------------------
\end{cventries}
